\documentclass{article}
\title{Site Files}

\usepackage[utf8x]{inputenc}
\usepackage[hebrew,english]{babel}
\usepackage{hebfont}

\begin{document}
\maketitle
In order to appear in the site you need to prepare several files.
One is mandatory, the others are optional (but highly recommended).
\begin{enumerate}
\item
	{\bf me.md}. 
	This is a YAML file (UTF-8 without bot).
	 There is no need to know what YAML is, as per the following example.
	CS staff must send the correct format.
	Due to the inherent limitations of some of the MATH staff idiotic formats (e.g., doc, pdf) are accepted
	by the current webmaster.
	\begin{tt}

---

\textvisiblespace \textvisiblespace \textvisiblespace staffType: faculty

\textvisiblespace \textvisiblespace \textvisiblespace firstName: First name

\textvisiblespace \textvisiblespace \textvisiblespace lastName: Family name

\textvisiblespace \textvisiblespace \textvisiblespace firstName\_he: \R{
שם פרטי
}

\textvisiblespace \textvisiblespace \textvisiblespace lastName\_he: \R{
שם משפחה
}

\textvisiblespace \textvisiblespace \textvisiblespace researchTopics: Topic1, Topic2, ...

\textvisiblespace \textvisiblespace \textvisiblespace teachingTopics: Topics1, Topics, ...

\textvisiblespace \textvisiblespace \textvisiblespace researchTopics\_he: \R{
נושא1, נושא2, ...
}

\textvisiblespace \textvisiblespace \textvisiblespace teachingTopics\_he:\R{
 נושא1, נושא2, ...
}

\textvisiblespace \textvisiblespace \textvisiblespace room: xxx

\textvisiblespace \textvisiblespace \textvisiblespace email: ...

\textvisiblespace \textvisiblespace \textvisiblespace personalSite: https://www.dns.somewhere/\textasciitilde mepage

\textvisiblespace \textvisiblespace \textvisiblespace oldPersonalSite: https://www.dns.somewhere/\textasciitilde mepage

\textvisiblespace \textvisiblespace \textvisiblespace born: "19??-??-??"

\textvisiblespace \textvisiblespace \textvisiblespace rank: 4

\textvisiblespace \textvisiblespace \textvisiblespace formerDean: false

\textvisiblespace \textvisiblespace \textvisiblespace emeritus: false

\textvisiblespace \textvisiblespace \textvisiblespace passedAway: "20??-??-??"

---

	\end{tt}
Files without the first nine fields will be ignored by the webmaster.
There are reasonable defaults for the other fields.
Still it is recommended to fill in everything.
You will be forgiven if the {\tt passAway} field remains empty or is completely dropped.
Anyways it is reasonable to expect the next death will be of the webmaster.
(Any volunteers for this thanksless position?)

\item
	{\bf me.png} or {\bf me.jpg}. Head photo. 
	If you have some other format (why?) it might be possible to handle it as well.

\item
  {\bf \textunderscore me.bib}.
	This is your publications list file.
	It stands to reason that anyone here uses {\LaTeX}  hence knows what a {\bf bibtex/biblatex} files are.
   The parser used to read the bib seems to be doing a reasonable job.
	However, it is a work in eternal progress, hence if there are problems (or missing features),
		please inform the webmaster.

\item
	{\bf meGloria.html/meGloria.md}.
		This is your self page if so you wish.
	It can be either an html file or a markdown file.
	You can send several files with links, subdirectories, etc., in a .zip file if you want a glorified
	self page.
\end{enumerate}
\end{document}